GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-10-10 paper/kbanotebook2013/content/implementation.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass
Rearranged a lot of text. Still need to fix the language

\subsection{Streaming Slot Value Extraction}

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
\includegraphics[width=6in]{./images/Pattern.eps}
\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
\vspace*{-.2in}
\end{figure}

@@

 The type of slot values could be the entity 
type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
hard-code. For these three kinds of patterns, we implement them in different 
ways accordingly. Next we will explain the patterns with more details, a brief example can be found in Figure \ref{fig:pattern}.

@@

For accuracy, we have found that there are three major kinds of errors: First,  
wrong entities found; next, wrong tags by the Lingpipe; and finally wrong results matched 
by the patterns. We solve the first problem by using the Wikipedia or twitter 
information of the entities to get better alias names. And we use
post-processing to reduce the second and third types of errors (Section \ref{section:highAccuracyFilter}).

>>>>

\subsection{Cumulative Citation Recommendation}
\label{sec:ccrimpl}

Our pipeline of processing the corpus consists of a two layer indexing system 
referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
Chunk Files Index Generator will generate indexes of the chunk files 
that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity 
respectively. This two level indexing will eliminate the need to process each and 
every ChunkFile/StreamItem for every entity. The reason for splitting this task 
into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which 
is written in C++ will discard non-mentioning chunk files and will stop further 
processing a chunk file as soon as it finds a mention there. Each chunk file can 
contain up to thousands of SIs which can be so time consuming if we were to 
process them in our Java base code.Processing StreamItems on the other hand is 
done in Java with ideas in mind for later on extensibility by adding other Java libraries.

\subsection{Streaming Slot Value Extraction}
\label{sec:ssve}
\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\vspace*{-.1in} \caption{Pattern Matching with Slot Value on the Right Side of Entity. }\label{fig:pattern}
\vspace*{-.2in}
\end{figure}

@@

 The type of slot values could be the entity 
type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
hard-code. For these three kinds of patterns, we implement them in different 
ways accordingly. Next we will explain the patterns with more details, a brief
example can be found in Figure~\ref{fig:pattern}.

@@

For accuracy, we have found that there are three major kinds of errors: First,  
wrong entities found; next, wrong tags by the Lingpipe; and finally wrong results matched 
by the patterns. We solve the first problem by using the Wikipedia or twitter 
information of the entities to get better alias names. And we use
post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).

### 2013-10-10 paper/kbanotebook2013/content/introduction.tex
Rearranged a lot of text. Still need to fix the language

Given a set of entities, possible citations may come from a large variety of sources.
To attack this problem we develop a system to read streaming data and
filter out articles that are candidates for citations.
Given these documents, we extract the pairs of information in the 
article that is recommended for citations.

Our system contains three main components. First, we pre-process the data and
build models representing the knowledge base entries.
Next, we use the models to filter a stream of documents so they only contain 
candidate recommendations.
Lastly, we processes sentences from candidate extractions and return 
specific information to be cited.

We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
The data set from this task drop most our our design systems.
Overall, our contributions are the following:
\begin{itemize}[noitemsep,nolistsep]
\item we built a system to filter a large amount of diverse documents (Section~\ref{},\ref{});
\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{},\ref{});
\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{},\ref{}).
\end{itemize}

\section{KBA Task Background\ceg{Move this to appendix?}}
\label{sec:kbatask}
The National Institute of Standards (NIST) hosted the
Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
contains two main sections designed for this track, Cumulative Citation Recommendation 
and Streaming Slot Filling. Due to the importance of knowledgebases, both of these 
tracks aim to accelerating populating them, hence the title Knowledgebase Acceleration (KBA).
Below we describe each of these tracks and their purposes.

>>>>

Given an entity page, possible citations may come from a variety of sources.
The actual citable information is a small percentage of the total documents that appear on the web.
We develop a system to read streaming data and filter out articles that are candidates for citations.
Given these documents, we extract the pairs of information in the 
article that is recommended for citations for each knowledge base page.
\ceg{add details}

Our system contains three main components. First, we pre-process the data and
build models representing the knowledge base entries.
Next, we use the models to filter a stream of documents so they only contain 
candidate recommendations.
Lastly, we processes sentences from candidate extractions and return 
specific information to be cited.
\ceg{add details}

We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
The data set from this task drop most our our design systems.
Overall, our contributions are the following:
\begin{itemize}[noitemsep,nolistsep]
\item we introduce a method to build models of name variations (Section~\ref{sec:preproc},~\ref{section:aliasgeneration});
\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccr1},~\ref{sec:ccrimpl});
\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssf1},~\ref{sec:ssve});
\item we filter the final results using deduplication and inference (Section~\ref{sec:postproc},~\ref{section:highAccuracyFilter});
\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
\end{itemize}

\section{KBA Task Background\ceg{Move this to appendix?}}
\label{sec:kbatask}
The National Institute of Standards (NIST) hosted the
Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
contains two main sections designed for this track, Cumulative Citation Recommendation 
and Streaming Slot Filling. Due to the importance of knowledge bases, both of these 
tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA).
Below we describe each of these tracks and their purposes.

### 2013-10-10 paper/kbanotebook2013/content/results.tex
Rearranged a lot of text. Still need to fix the language

\section{Results}

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was composed of a single node cluster, which we refer to as the \textit{server}; the configuration of which is as described in Table \ref{table:serverspec}. The corpus is a snapshot of the web in English. Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. The total size of the data after XZ compression and GPG encryption is 4.5TB and just over 500M StreamItems \cite{s3}. Data is stored in directories the naming of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am) until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952 date-hour combinations. This corpora consists of various media types the distribution of which can be found in \ref{table:documentsDist}. To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2012 is considered as training data. The source code of our system is stored as an open source project where enthusiasts can also contribute to \cite{github}, also the relevant discussion mailing list is accessible here \cite{googlegroups}.

@@

On the performance of the first submission run we performed random 
sampling via two processes, the results of which are according to Table \ref{table:initialresult}. You can view that we have had an accuracy of around 55\%, and about 15\% wrong entity identified and 30\% incorrect value extracted across all entities and slot types. For our final submission, we provide a more detailed statistics, which has been elaborated in Tables \ref{table:finalresultrecall} and \ref{table:finalresultaccuracy}. Table \ref{table:finalresultrecall} shows the extent of search outreach for each slot name. You can see that \textit{Affiliate} has been the slot name with highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found matching our patterns, after that \textit{AwardsWon} has been the next with 38 instances found. Table \ref{table:finalresultaccuracy} addresses the relative accuracy measure per slot value. There you can view that we have had the highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of 1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.

>>>>

\section{Results}
\label{sec:results}

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was composed of a single node cluster, which we refer to as the
 \textit{server}; the configuration of which is as described in
 Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
 Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
The total size of the data after XZ compression and GPG encryption is 4.5TB and
just over 500M StreamItems \cite{s3}. Data is stored in directories the naming
of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am)
until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952
date-hour combinations. This corpora consists of various media types the
distribution of which can be found in Table~\ref{table:documentsDist}. To have a
sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2012 is considered as training data.
The source code of our system is stored as an open source project where
enthusiasts can also contribute to \cite{github}, also the relevant discussion
mailing list is accessible here \cite{googlegroups}.

@@

On the performance of the first submission run we performed random 
sampling via two processes, the results of which are according to
Table~\ref{table:initialresult}. You can view that we have had an accuracy of
around 55\%, and about 15\% wrong entity identified and 30\% incorrect value
extracted across all entities and slot types. For our final submission, we
provide a more detailed statistics, which has been elaborated in
Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
Table~\ref{table:finalresultrecall} shows the extent of search outreach for
each slot name. You can see that \textit{Affiliate} has been the slot name with
highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found
matching our patterns, after that \textit{AwardsWon} has been the next with 38
instances found. Table~\ref{table:finalresultaccuracy} addresses the relative
accuracy measure per slot value. There you can view that we have had the
highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of
1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.

### 2013-10-10 paper/kbanotebook2013/content/system.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass
Rearranged a lot of text. Still need to fix the language

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
\includegraphics[width=6in]{./images/sdl.eps}
% http://convert.neevia.com/pdfconvert/
%SystemDiagramLanguages-pdf.eps
\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
\vspace*{-.2in}
\end{figure}

@@

In this section, we sketch out the main components of the system. Our system is built with a pipeline architecture in mind which gives it the advantage to run each section separately and allow stream processing without resources being wasted by one operation while others are awaiting (Figure \ref{fig:system}). This consists of a section to perform pre-processing to prepare the required data, Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming Slot Filling which generates the actual slot values and Post processing to increase precision/recall.

@@

\subsection{Preprocessing}

To begin, we need to have real-world aliases of entities of interest. TREC KBA prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways. We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity. We also extract  aliases from within the text of a wiki entity, which will be described in Section \ref{section:aliasgeneration}. This whole process is referred to as \textit{Alias Extraction}. On the other hand, regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them. Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract alias out of tweets or entities descriptions in their profiles. This process of extracting aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

@@

\subsection{CCR}

@@

Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.  Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities. StreamItems Index Generator on the other hand will index StreamItems that contain a mention of a given entity respectively. This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity. The reason for splitting this task into two steps is that not all chunk files contain any mention of the entities and we want to get rid of them as soon as possible. Chunk Files Index Generator which is written in C++ will discard non-mentioning chunk files and will stop further processing a chunk file as soon as it finds a mention there. Each chunk file can contain up to thousands of SIs which can be so time consuming if we were to process them in our Java base code.Processing StreamItems on the other hand is done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

\subsection{SSF}
%\ceg{See the previous note.}
The purpose of slot filling is to extract proper values for relations of interest, which can be found in Table \ref{table:slotNameOntology}. This is called Stream Slot Filling because data is being generated as time goes on and for each extraction we should only consider current or past data. In figure \ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}. Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

\subsection{Post Processing Algorithm}

>>>>

\begin{figure}
\centering
%\includegraphics[width=6in]{./images/sdl.eps}
\includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
% http://convert.neevia.com/pdfconvert/
\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
\vspace*{-.2in}
\end{figure}

@@

In this section, we sketch out the main components of the system. Our system is 
built with a pipeline architecture in mind which gives it the advantage to run 
each section separately and allow stream processing without resources being wasted 
by one operation while others are awaiting (Figure~\ref{fig:system}).
This consists of a section to perform pre-processing to prepare the required data, 
Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
Slot Filling which generates the actual slot values and Post processing to 
increase precision/recall.

@@

\subsection{Preprocessing}
\label{sec:preproc}

To begin, we need to have real-world aliases of entities of interest. TREC KBA
prohibits Wikipedia entities to have any manual aliases being added and only
allows automatic ways. We use Wikipedia API backlink references
(redirects to a wiki entity) as aliases of the entity. We also extract 
aliases from within the text of a wiki entity, which will be described in
Section~\ref{section:aliasgeneration}. This whole process is referred to as
\textit{Alias Extraction}. On the other hand, regarding Twitter entities this
limit is lifted and participants are allowed to manually add aliases for them.
Part of the reason is that Twitter environment is composed of so much informal
and dialectic language which makes it extremely difficult to extract alias out
of tweets or entities descriptions in their profiles. This process of extracting
aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

@@

\subsection{CCR}
\label{sec:ccr1}

@@

@@

\subsection{SSF}
\label{sec:ssf1}
%\ceg{See the previous note.}
The purpose of slot filling is to extract proper values for relations of
interest, which can be found in Table~\ref{table:slotNameOntology}.
This is called Stream Slot Filling because data is being generated as time goes
on and for each extraction we should only consider current or past data.
In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

\subsection{Post Processing Algorithm}
\label{sec:postproc}

### 2013-10-10 paper/kbanotebook2013/paper.tex
Updated citations so they compile correctly. Changed the figure resources so they compile easily with pdflatex. I updated the introduction to make it a little more indepth. I still have more work to do when making this pass
Rearranged a lot of text. Still need to fix the language

\usepackage{xcolor}
\usepackage{cite }
\usepackage{graphicx, epsfig}
\usepackage[margin=1in]{geometry}
\usepackage[hyphens]{url}

@@

\author {
 Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{ University of Florida, Gainesville, Florida, USA}\\
       { \{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
\and
  Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
       {mpetrovic@ihmc.us}
}

>>>>

\usepackage{xcolor}
\usepackage{cite }
\usepackage{graphicx, epsfig}
\usepackage[margin=1in]{geometry}
\usepackage[hyphens]{url}
\usepackage{enumitem}

@@

\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}\\
       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
\and
  Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
       {mpetrovic@ihmc.us}
}
